```{r}
require(knitr)
opts_knit$set(root.dir = "~/Desktop/Dropbox/PhD/R_Projects/RUN-WGCNA/")
```


RUN-WGCNA
========================================================
#Wrapper functions to perform a quick preliminary weighted-gene co-expression network analysis

###Background

###Preliminaries
First you need to ensure you have all the required R libraries to run these wrapper functions. 
```{r, eval=FALSE}
source("http://bioconductor.org/biocLite.R")
biocLite(c("AnnotationDbi", "impute", "GO.db", "preprocessCore"))
install.packages(pkgs=c("WGCNA", "flashClust", "ggplot2"))
```

Load the libraries and wrapper scripts
```{r}
source("WGCNA_functions.R")
library(reshape2)
library(ggplot2)
```

Load the example data
```{r, cache=TRUE}
dat <- read.table(file="exprsExtimates.csv", header=TRUE, row.names=1, sep=",")
```

###Running a co-expression analysis

First, we need to determine levels of connectivity at different powers
```{r, cache=TRUE}
determineSoftPowerWGCNA(data1=dat, outFile="plots/powerPlots.pdf",
                        propGenes=0.33)
```
![](plots/powerPlots.pdf)

Assemble to nework with the chosen power
```{r, cache=TRUE}
net <- runWGCNA(data1=dat, propGenes=0.33, softPower=6, signedNetwork=TRUE)
rm(dat)
```

Now assemble the network and look at the modules with different dynamic tree cut hights
```{r, cache=TRUE}
plotModulesCut(referenceDataset=net, outFile="plots/modClusterPlot.pdf")
```
![](plots/modClusterPlot.pdf)

Calculate the eigengenes
```{r, cache=TRUE}
e1 <- calculateModuleEigengenes(referenceDataset=net, split=2)
```

Plot the eigengene expression for each experimental group and co-epxression module
```{r, cache=TRUE}
groups <- gsub('.{2}$', '', x=rownames(e1))
groups <- t(data.frame(strsplit(groups, split=".", fixed=TRUE)))
colnames(groups) <- c("Oxygen", "Media")
groups[ ,1] <- gsub('X', '', groups[ ,1])
rownames(groups) <- NULL
e1 <- cbind(e1, groups)

melted <- melt(data=e1, id.vars=c("Oxygen", "Media"))
melted$Oxygen <- gsub(pattern="pc", replacement="", melted$Oxygen)
melted <- melted[order(as.numeric(melted$Oxygen)), ]

pdf(file="plots/eigengenBoxplots.pdf", width=12)
q <- qplot(data=melted, y=value, x=Oxygen, facets=Media~variable, 
           geom=c("boxplot", "point"), ylab="Eignegene expression",
           colour=Oxygen)
q + scale_x_discrete(limits=c("1","5","20"))
dev.off()
```
![](plots/eigengenBoxplots.pdf)




